\documentclass[../../main.tex]{subfiles}
\begin{document}

The purpose of this document is to formalize, justify, and explain the design of this software. The associated code is primarily concerned with the evolution of entities in a 3D environment. The decisions laid out in this document are to justify their design with the aim of usability, extendability, and maintainability.


\section{Context}
	The evolutionary algorithm is exciting due to the relatively unpredictable behavior, while being able to solve difficult problems. On top of this, neural networks have also become increasing popular with their applications ranging across almost every technological domain. Thus a combination is surely worth exploring. Despite this, there are few examples where these are combined in the evolution of entities in a 3D environment, with sufficient interaction from the user. Thus, this software finds its place there.

	% \begin{itemize}
	% 	\item \href{https://www.youtube.com/watch?v=GOFws_hhZs8}{\faVideoCamera Carykh - Evolution Simulator}
	% 	\item \href{https://www.youtube.com/watch?v=r_It_X7v-1E}{\faVideoCamera Sebastian Lague - Simulating an Ecosystem}
	% 	\item \href{https://www.youtube.com/watch?v=0ZGbIKd0XrM}{\faVideoCamera Primer - Simulating Natural Selection}
	% 	\item \href{https://www.spore.com/}{\faGamepad Spore}
	% 	\item \href{http://www.speciesgame.com}{\faGamepad Species: Artificial Life, Real Evolution}
	% \end{itemize}

\section{Goals and Non-Goals}
	The goal of this software is not exactly pinned down. It may end up as a simulator or a game. The development so far would lend itself well to controlling a single creature in a competitive environment. Possibly the user could guide the evolution, or unlock upgrades / augmentations as their creature completes tasks / progresses. Once the prerequisite problems have been solved, more consideration would be added. Regardless, real-time evolution is an important aspect.

	There are several tools, algorithms, theories, and techniques that are required to get all the machinery working. As a result, this provides a good opportunity to learn about physics, machine learning, and software design. Although not a primary focus, knowledge of 3D graphics is required to create a visually appealing environment. Other considerations like audio could also be implemented. These are largely considerations for the future, since the graphics will likely be ported over to \href{https://unity.com/}{Unity} when  a base use has been established. Far in the future, online play with a database, levels etc. may be added.

\end{document}